### 2025-11-24 multiple-regression.qmd
20251124 - covariates

>>>>

However, it is worth noting that, for several reasons, including a variable as a covariate in a model does not necessarily fully control for that construct.
First, your measure of the covariate has measurement error and may not fully capture the construct, which can lead to [residual confounding](#sec-causalDiagramConfounding).
Second, including the covariate only accounts for the linear effect of that variable.
The variable (e.g., age) could have nonlinear effects that are not captured by the linear term (and may require nonlinear terms, e.g., quadratic).
Third, the construct could interact with other constructs, which would also not be captured by the linear term (and may require interaction terms).
Thus, it is important to consider the reliability of the covariate, and the ways in which the covariate is related to the outcome including any nonlinearity and interactions.
